Mentored data science research with tweets

### 2020-04-18 Rmd/jse-2019-ms.Rmd
updated manuscript; added todo file

```{r child = "introduction.Rmd"}
```

```{r child = "methods.Rmd"}
```

>>>>

## Introduction

Twitter has changed the way that we communicate. 
In only 140 characters, users speak their piece on politics, 
current events, sports, media, and many other topics. 
Recent development of accessible statistical methods for text 
analysis now enable instructors to use tweets as pedagogical 
tools in mentoring undergraduate research projects.

Some social media data, including tweets from Twitter, are 
available through website application product interfaces (APIs). Twitter 
shares, via a streaming API, a sample of approximately one percent of all 
tweets during an API query time period [@tweet_stream].
Researchers have studied tweets for a 
variety of purposes, including 
inference of relationships and social networks among users [@lin2011joint]; 
determination of 
authorship of specific tweets when multiple persons share a single account [@drob]; and 
study of rhetoric in recruiting political supporters [@pelled2018little;@wells2016trump].
Recognizing the potential utility of tweets for data science research and teaching, 
we created a 
collection of tweets over time by repeated querying of the Twitter streaming API.

@nolan2010computing argue for students to work with real data. 
Working with real data allows students to develop skill not only in statistical analysis,
but also in related data science skills, including data transfer from online sources, data storage, and using data 
from multiple file formats.

Mentoring in the work place and in higher education can have many 
benefits, including improving students' development as thinkers and scholars, confidence in their 
own abilities, integration into the campus community,
and interest in graduate training 
[@baker2010beyond;@higgins2001reconceptualizing].

We present below 1) an approach for collecting tweets in real 
time and 2) statistical methods for detecting social media 
events via topic modeling of tweets and 3) reflections on 
using this data set in research mentoring for undergraduate 
students.

## Methods
